An Experimental Analysis of the Influence of the Precision of Parameters in an Artificial Neural Network

### 2025-07-16 paper/main.tex
completed summary

	\item \textbf{Mixed-Precision:} Training and Gradient Clipping: TODO

>>>>

	\item \textbf{Mixed-Precision:} Training with mixed precision and Gradient Clipping
		  resulted in similar test accuracy scores as precision reduction during training
		  as well as post-training quantization. No significant decrease in model
		  performance accuracy was detected. The train and test times were similar,
		  regardless of using FP32, FP16 or a mix of both.
